---
date: "2024-10-02"
output: html_document
---

```{r clean_start}
rm(list = ls())

# Color palette
media_colors <- c("#d69d10", "#000000", "#cc0000", "#05b2fc")
Sys.setlocale("LC_TIME", "en_US.UTF-8")

## Load required libraries 
require(tidyverse)
require(plotly)
require(purrr)
library(patchwork)
library(grid)
library(jpeg)
library(rlang)
```


## define the colors


```{r}
BBC_black <-  "#000000"
CNN_red <- "#cc0000"
AJ_yellow <- "#d69d10"
AJ_blue <- "#1d174e"
DW_blue <- "#05b2fc"
media_colors <- c("#d69d10", "#000000", "#cc0000", "#05b2fc")
# Define the custom colors and shapes for each source
source_colors <- c("en_BBCNews" = "#000000", "en_CNN" = "#cc0000", "en_AJ" = "#d69d10", "en_DW" = "#05b2fc")
source_colors2 <- c("BBC" = "#000000", "CNN" = "#cc0000", "AJ" = "#d69d10", "DW" = "#05b2fc")
source_shapes <- c("en_BBCNews" = 15, "en_CNN" = 17, "en_AJ" = 18, "en_DW" = 19)  # Assign different shapes
source_shapes2 <- c("BBC" = 15, "CNN" = 17, "AJ" = 18, "DW" = 19)  # Assign different shapes
```


## import the data
```{r}
  en_AJ <- read.csv("killed_data/en_AJ_killed-murdered.csv")%>% 
  mutate(publish_date = as.Date(as.character(publish_date), format="%Y%m%d"))
en_BBCNews <- read.csv("killed_data/en_BBCNews_killed-murdered.csv")%>% 
  mutate(publish_date = as.Date(as.character(publish_date), format="%Y%m%d"))
en_CNN <- read.csv("killed_data/en_CNN_killed-murdered.csv")%>% 
  mutate(publish_date = as.Date(as.character(publish_date), format="%Y%m%d"))
en_DW <- read_csv("killed_data/en_DW_killed-murdered.csv") %>% 
  mutate(publish_date = as.Date(as.character(publish_date), format="%Y%m%d"))
```

## filter data
We only want the data after the 7th October
```{r}
en_AJ <- en_AJ %>% filter(publish_date > "2023-08-07")
en_BBCNews <- en_BBCNews %>% filter(publish_date > "2023-08-07")
en_CNN <- en_CNN %>% filter(publish_date > "2023-08-07")
en_DW <- en_DW %>% filter(publish_date > "2023-08-07")

```



## Create function to count column_name
```{r}
simple_count_subjects <- function(data, column_name) {
  # Split the strings into individual words and unlist them
  subjects <- unlist(strsplit(data[[column_name]], " "))
  
  # Count the occurrences of each unique string
  subjects_counts <- table(subjects)
  
  # Convert to a data frame for easier viewing
  subjects_counts_df <- as.data.frame(subjects_counts)
  colnames(subjects_counts_df) <- c("String", "Count")
  
  # Calculate the percentage
  subjects_counts_df$Percentage <- round((subjects_counts_df$Count / sum(subjects_counts_df$Count)) * 100, 2)
  
  return(subjects_counts_df)
}
```

```{r}
count_per_date_subjects <- function(data, column_name) {
  # Create an empty data frame to store results
  results_df <- data.frame(String = character(), publish_date = as.Date(character()), total_word_count = numeric(), stringsAsFactors = FALSE)
  
  # Loop over each row of the data frame
  for (i in 1:nrow(data)) {
    # Get the publish_date, total_word_count, and text column for the current row
    current_date <- data$publish_date[i]
    total_words <- data$total_word_count[i]
    text_entry <- data[[column_name]][i]
    
    # Check if text_entry, current_date, or total_word_count is NA
    if (is.na(text_entry) | is.na(current_date) | is.na(total_words)) {
      next  # Skip this iteration if there are missing values
    }
    
    # Split the strings into individual words
    words <- unlist(strsplit(text_entry, " "))
    
    # Remove empty strings and NA values
    words <- words[!is.na(words) & words != ""]
    
    # Only proceed if there are words
    if (length(words) > 0) {
      # Create a data frame with the words and their associated publish_date and total_word_count
      temp_df <- data.frame(String = words, publish_date = current_date, total_word_count = total_words, stringsAsFactors = FALSE)
      
      # Combine this with the main results data frame
      results_df <- rbind(results_df, temp_df)
    }
  }
  
  # Count occurrences of each unique string per publish_date
  subjects_counts_df <- results_df %>%
    group_by(String, publish_date, total_word_count) %>%
    summarise(Count = n(), .groups = 'drop')
  
  # Calculate instances per million for each word per publish_date
  subjects_counts_df$Instances_Per_Million <- (subjects_counts_df$Count / subjects_counts_df$total_word_count) * 1e6
  
  # Calculate the overall total count of each string across the entire dataset
  total_counts <- results_df %>%
    group_by(String) %>%
    summarise(TotalCount = n(), .groups = 'drop')
  
  # Calculate the overall percentage for each word across the entire dataset
  total_count_all_words <- sum(total_counts$TotalCount)
  total_counts$Total_Percentage <- round((total_counts$TotalCount / total_count_all_words) * 100, 2)
  
  # Merge the total percentage information back to the main results
  subjects_counts_df <- merge(subjects_counts_df, total_counts[, c("String", "Total_Percentage")], by = "String", all.x = TRUE)
  
  return(subjects_counts_df)
}


```

normalize the strings in the "killed.VVN.subject" column
```{r}
library(dplyr)
library(stringr)
#library(tm)  # For removing stop words

# Example function to normalize the "killed.VVN.subject" column
normalize_text <- function(text) {
  text <- tolower(text)  # Convert to lowercase
  text <- str_replace_all(text, "[[:punct:]]", " ")  # Remove punctuation
  text <- str_squish(text)  # Remove extra whitespace
#  text <- removeWords(text, stopwords("en"))  # Remove common English stop words
  return(text)
}

# Apply normalization to the relevant columns
en_AJ$killed.VVN.subject <- sapply(en_AJ$killed.VVN.subject, normalize_text)
en_BBCNews$killed.VVN.subject <- sapply(en_BBCNews$killed.VVN.subject, normalize_text)
en_CNN$killed.VVN.subject <- sapply(en_CNN$killed.VVN.subject, normalize_text)
en_DW$killed.VVN.subject <- sapply(en_DW$killed.VVN.subject, normalize_text)

```

## Count the strings in col = "killed.VVN.subject"
```{r}
en_AJ_killed_subjects_counts_df <- simple_count_subjects(en_AJ, "killed.VVN.subject")
en_BBCNews_killed_subjects_counts_df <- simple_count_subjects(en_BBCNews, "killed.VVN.subject")
en_CNN_killed_subjects_counts_df <- simple_count_subjects(en_CNN, "killed.VVN.subject")
en_DW_killed_subjects_counts_df <- simple_count_subjects(en_DW, "killed.VVN.subject")
# Apply the function to each of your data frames
en_AJ_killed_subjects_date_counts_df <- count_per_date_subjects(en_AJ, "killed.VVN.subject")
en_BBCNews_killed_subjects_date_counts_df <- count_per_date_subjects(en_BBCNews, "killed.VVN.subject")
en_CNN_killed_subjects_date_counts_df <- count_per_date_subjects(en_CNN, "killed.VVN.subject")
en_DW_killed_subjects_date_counts_df <- count_per_date_subjects(en_DW, "killed.VVN.subject")
```

```{r}
# Assign names to the data frames
killed_dfs <- list(
  en_AJ = en_AJ_killed_subjects_counts_df, 
  en_BBCNews = en_BBCNews_killed_subjects_counts_df, 
  en_CNN = en_CNN_killed_subjects_counts_df, 
  en_DW = en_DW_killed_subjects_counts_df
)

# Sort each data frame by Count in descending order
killed_dfs_sorted <- map(killed_dfs, ~ arrange(.x, desc(Count)))

# Rename 'Count' column with the respective data frame name
killed_dfs_named <- imap(killed_dfs_sorted, ~ rename(.x, !!.y := Count))

# Combine the data frames using full_join by "String"
combined_killed_subject <- reduce(killed_dfs_named, full_join, by = "String")
```


```{r}
process_frequency_data <- function(df, media_name) {
  df %>%
    arrange(publish_date, .by_group = TRUE) %>%
    mutate(count_killed_acum = cumsum(Count)) %>%
    mutate(count_killed_max = max(count_killed_acum)) %>%
    mutate(slope = (count_killed_acum - lag(count_killed_acum)) / as.numeric(publish_date - lag(publish_date)))%>%
    ungroup() %>%
    mutate(log_count_killed_acum = log(count_killed_acum + 1)) %>%
    mutate(media = media_name)
}
```

```{r}
en_AJ_killed_subjects_date_counts_df <- process_frequency_data(en_AJ_killed_subjects_date_counts_df, "AJ")
en_BBCNews_killed_subjects_date_counts_df <- process_frequency_data(en_BBCNews_killed_subjects_date_counts_df, "BBC")
en_CNN_killed_subjects_date_counts_df <- process_frequency_data(en_CNN_killed_subjects_date_counts_df, "CNN")
en_DW_killed_subjects_date_counts_df <- process_frequency_data(en_DW_killed_subjects_date_counts_df, "DW")
```

```{r}
combined_killed_subject_date <- rbind(en_AJ_killed_subjects_date_counts_df,en_BBCNews_killed_subjects_date_counts_df,en_CNN_killed_subjects_date_counts_df,en_DW_killed_subjects_date_counts_df)
```

```{r}
combined_killed_subject_date <- combined_killed_subject_date %>% arrange(desc(Total_Percentage))

# Words to exclude
words_to_exclude <- c("who", "that", "he", "they", "have", "palestinian","to")

# Filter out the words to exclude
df_filtered <- combined_killed_subject_date[!combined_killed_subject_date$String %in% words_to_exclude, ]

# Get the first 10 unique strings
unique_strings <- unique(df_filtered$String)[1:5]

# Subset the filtered data frame based on these 10 unique strings
subset_df <- df_filtered[df_filtered$String %in% unique_strings, ]

subset_df <- subset_df %>% rename(Subjects = String)
```


```{r}
# Add publish_month column
subset_df <- subset_df %>%
  mutate(publish_month = format(publish_date, "%Y-%m"))
```

##summarize for month
```{r}
summary_df <- subset_df %>%
  group_by(Subjects, publish_month, media) %>%
  summarise(
    total_word_count = sum(total_word_count, na.rm = TRUE),
    Count = sum(Count, na.rm = TRUE),
    Instances_Per_Million = mean(Instances_Per_Million, na.rm = TRUE),
    #Total_Percentage = mean(Total_Percentage, na.rm = TRUE),
    #count_killed_acum = max(count_killed_acum, na.rm = TRUE),
    #count_killed_max = max(count_killed_max, na.rm = TRUE),
    #slope = mean(slope, na.rm = TRUE),
    #log_count_killed_acum = mean(log_count_killed_acum, na.rm = TRUE)
  )
```
```{r}
filtered_subset_df <- summary_df %>% filter(Subjects=="palestinians")
```


```{r}
ggplotly(ggplot(filtered_subset_df, aes(x = publish_month, y = Instances_Per_Million , fill = media)) +
    #geom_vline(xintercept = as.Date(date_to_plot), linetype = "dashed") +
    geom_col(alpha = 0.7) +
    #geom_point()+
    theme_minimal() +
    theme(panel.grid = element_blank()) +
    #scale_color_manual(values = source_colors2) +
    scale_fill_manual(values = media_colors) +
    xlab("") +
    ylab("Mentions")+
  facet_grid(rows = vars(media)))
```

```{r}
#ggplotly(ggplot(summary_df, aes(x = publish_month, y = count_killed_acum/count_killed_max , fill = Subjects)) +
#    #geom_vline(xintercept = as.Date(date_to_plot), linetype = "dashed") +
#    geom_col(alpha = 0.7) +
 #   theme_minimal() +
 #   theme(panel.grid = element_blank()) +
 #   #scale_fill_manual(values = media_colors) +
 #   xlab("") +
  #  ylab("Mentions")+
#  facet_grid(rows = vars(media)))
```


```{r}
# Make sure the dataset is sorted based on the relevant column (e.g., en_AJ, en_BBCNews, en_CNN, etc.)
combined_killed_subject <- combined_killed_subject %>% arrange(desc(en_AJ))

# Select the top 10 rows for visualization
top10_combined <- combined_killed_subject[1:10, ]

# Reshape data to long format
top10_long <- top10_combined %>%
  pivot_longer(
    cols = starts_with("en_"), 
    names_to = "media", 
    values_to = "Count"
  ) %>%
  filter(!is.na(Count))  # Filter out rows with NA values

# Extract the corresponding percentage columns for each source and pivot them as well
percentage_long <- top10_combined %>%
  select(String, starts_with("Percentage")) %>%
  pivot_longer(
    cols = starts_with("Percentage"),
    names_to = "media",
    values_to = "Percentage"
  )

# Clean the 'Source' column to match the original data frame names (e.g., "Percentage.x" to "en_AJ")
percentage_long$Source <- gsub("Percentage\\.", "", percentage_long$media)
percentage_long$Source <- recode(percentage_long$media,
                                 "x" = "en_AJ", 
                                 "y" = "en_BBCNews", 
                                 "x.x" = "en_CNN", 
                                 "y.y" = "en_DW")

# Join the long-format data frames
top10_long <- top10_long %>%
  left_join(percentage_long, by = c("String", "media"))

# Remove the "en_" prefix and change "BBCNews" to "BBC" in the 'media' column of the main dataset
top10_long$media <- gsub("^en_", "", top10_long$media)
top10_long$media <- gsub("BBCNews", "BBC", top10_long$media)

# Sort the x-axis by the percentage in descending order
top10_long <- top10_long %>%
  arrange(desc(Percentage)) %>%
  mutate(String = factor(String, levels = unique(String), ordered = TRUE))


```




```{r}
# Define your list of words to filter out
words_to_exclude <- c("who", "that", "he","they","have","palestinian")  # Replace with the actual words you want to exclude

# Make sure the dataset is sorted based on the relevant column (e.g., en_AJ, en_BBCNews, en_CNN, etc.)
combined_killed_subject <- combined_killed_subject %>% arrange(desc(en_AJ))

# Filter out words that are in the exclusion list
combined_killed_subject_filtered <- combined_killed_subject %>%
  filter(!String %in% words_to_exclude)

# Select the top 10 rows for visualization
top10_filtered_combined <- combined_killed_subject_filtered[1:10, ]

# Reshape data to long format
top10_filtered_long <- top10_filtered_combined %>%
  pivot_longer(
    cols = starts_with("en_"), 
    names_to = "media", 
    values_to = "Count"
  ) %>%
  filter(!is.na(Count))  # Filter out rows with NA values

# Extract the corresponding percentage columns for each source and pivot them as well
percentage_long <- top10_filtered_combined %>%
  select(String, starts_with("Percentage")) %>%
  pivot_longer(
    cols = starts_with("Percentage"),
    names_to = "media",
    values_to = "Percentage"
  )

# Clean the 'Source' column to match the original data frame names (e.g., "Percentage.x" to "en_AJ")
percentage_long$media <- gsub("Percentage\\.", "", percentage_long$media)
percentage_long$media <- recode(percentage_long$media,
                                 "x" = "en_AJ", 
                                 "y" = "en_BBCNews", 
                                 "x.x" = "en_CNN", 
                                 "y.y" = "en_DW")

# Join the long-format data frames
top10_filtered_long <- top10_filtered_long %>%
  left_join(percentage_long, by = c("String", "media"))

# Remove the "en_" prefix and change "BBCNews" to "BBC" in the 'media' column of the main dataset
top10_filtered_long$media <- gsub("^en_", "", top10_filtered_long$media)
top10_filtered_long$media <- gsub("BBCNews", "BBC", top10_filtered_long$media)

# Sort the x-axis by the percentage in descending order
top10_filtered_long <- top10_filtered_long %>%
  arrange(desc(Percentage)) %>%
  mutate(String = factor(String, levels = unique(String), ordered = TRUE))
```


```{r}
# Calculate total word count for each source
total_word_counts <- top10_filtered_long %>%
  group_by(media) %>%
  summarise(total_word_count = sum(Count))

# Create a named vector for source colors and shapes with total counts in parentheses
source_labels <- total_word_counts %>%
  mutate(label = paste(media," ", "(", total_word_count, ")", sep = "")) %>%
  pull(label)

# Update the original color and shape mappings to include the counts in the labels
#names(source_colors) <- source_labels
#names(source_shapes) <- source_labels

# Update the Source column to match the new labels
#top10_filtered_long <- top10_filtered_long %>%
#  left_join(total_word_counts, by = "Source") %>%
#  mutate(Source = paste(Source, " (", total_word_count, ")", sep = ""))

# Create the ggplot with the updated y-axis label and the sum of total_word_count in the legend
plot <- ggplot(top10_filtered_long, aes(x = Percentage, y = String, color = media, shape = media, group = media)) +
  geom_point(size = 2) +
  scale_color_manual(values = source_colors2) +
  scale_shape_manual(values = source_shapes2) +
  labs(x = "Percentage", y = "Subjects", title = "Top 10 Subjects by Percentage from Different Sources") +
  scale_y_discrete(limits = rev(levels(top10_filtered_long$String)))+  # Reverse the y-axis to have the highest percentage at the top
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),  # Remove major vertical grid lines
    panel.grid.minor.x = element_blank()   # Remove minor vertical grid lines
  )
# Convert the ggplot to an interactive plotly plot
ggplotly(plot)
```
# Do the general frequency plot:

```{r}
# Define a function to arrange by publish_date and calculate the cumulative sum
process_dataframe <- function(df) {
  df <- df %>% 
    arrange(publish_date) %>%
    mutate(publish_month = format(publish_date, "%Y-%m")) %>%
    mutate(cum_killed = cumsum(killed.VVN.)) %>%
    mutate(count_killed_max = max(cum_killed)) %>%
  return(df)
}

# List of data frames
data_frames <- list(en_DW = en_DW, en_BBCNews = en_BBCNews, en_CNN = en_CNN, en_AJ = en_AJ)

# Apply the function to each data frame in the list
processed_data_frames <- lapply(data_frames, process_dataframe)

# Extract the processed data frames back into their original variables
en_DW <- processed_data_frames$en_DW
en_BBCNews <- processed_data_frames$en_BBCNews
en_CNN <- processed_data_frames$en_CNN
en_AJ <- processed_data_frames$en_AJ
```

```{r}
# Combine all processed data frames into one and calculate relative cum_killed
combined_data <- bind_rows(
  en_DW %>% mutate(media = "DW"),
  en_BBCNews %>% mutate(media = "BBC"),
  en_CNN %>% mutate(media = "CNN"),
  en_AJ %>% mutate(media = "AJ")
)

```


## function calculate cumulative frequency
```{r}
add_accum <- function(Colname, df){
  # Check if the column exists in the data
  if (!(Colname %in% colnames(df))) {
    stop(paste("Column", Colname, "not found in combined_channels"))
  }

  # Filter for lemma
  combined_accum <- df %>%
    group_by(media) %>%
    mutate(acccum_freq = cumsum(.data[[Colname]])) %>%  # Use .data[[Colname]] to access the column by name
        mutate(rel_acccum_freq = cumsum(.data[[Colname]])/cumsum(total_word_count)* 1e6) %>%  # Use .data[[Colname]] to access the column by name
    mutate(count_max = max(acccum_freq)) %>%
    ungroup()
    
  
  return(combined_accum)
}
```

```{r}
plot_lemma <- function(lemma, filtered_data, date_to_plot) {
  # Plotting
  filtered_data <- add_accum(lemma, filtered_data)
  plot1 <- filtered_data %>%
    ggplot(aes(x = publish_date, y = acccum_freq, color = media)) +
    geom_line() +
    theme_minimal() +
    theme(panel.grid = element_blank(),
          axis.text.x = element_blank()) +
    #scale_y_log10() +
    scale_color_manual(values = media_colors) +
    xlab("") +
    ylab("cumulative frequency") +
    geom_vline(xintercept = as.Date(date_to_plot), linetype = "dashed") +
    labs(title = paste0("Mentions of ", lemma," in media"))

  plot2 <- filtered_data %>%
    ggplot(aes(x = publish_date, y = rel_acccum_freq, color = media)) +
    geom_line() +
    geom_vline(xintercept = as.Date(date_to_plot), linetype = "dashed") +
    scale_color_manual(values = media_colors) +
    theme_minimal() +
    theme(panel.grid = element_blank()) +
    scale_x_date(date_labels = "%B %Y", date_breaks = "1 month")+
    theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    #axis.line.x = element_line(color = "black"),        # Ensure x-axis line is drawn
    axis.ticks.x = element_line(color = "black")        # Ensure x-axis ticks are shown
    )+
    scale_fill_manual(values = media_colors) +
    xlab("")+ 
    ylab("relative \n cumulative frequency (ipm)")

  # Align the plots by a common X axis
  aligned_plots <- plot1 / plot2

  # Display the aligned plots
  print(aligned_plots)
}
```



```{r}
 plots <- plot_lemma("killed.VVN.", combined_data, date_to_plot = c("2024-04-25", "2024-06-07"))
#ggsave("Passive_killed_general.pdf", scale = 0.6, plots,  width = 42,
#  height = 29.7, units="cm")
```

  

# Comparison casualties:
based on intro: https://en.wikipedia.org/wiki/Casualties_of_the_Israel%E2%80%93Hamas_war
```{r}

# Create the dataframe based on the provided statement
data <- data.frame(
  Category = c("Total Killed", 
               "Palestinian Killed", 
               "Israeli Killed", 
               "Journalists (Committee to Protect Journalists)", 
               "Palestinian Journalists", 
               "Israeli Journalists", 
               "Lebanese Journalists",
               "Journalists and Media Workers (International Federation of Journalists)", 
               "Palestinian Journalists and Media Workers", 
               "Israeli Journalists and Media Workers", 
               "Lebanese Journalists and Media Workers", 
               "Humanitarian Aid Workers", 
               "UNRWA Employees"),
  Count = c(43000, 41431, 1706, 116, 111, 2, 3, 134, 127, 4, 3, 224, 179)
)


```

```{r}
# Create the dataframe based on the updated summary table
summary_data <- data.frame(
  String = c("people", 
               "palestinians", 
               "civilians", 
               "children", 
               "workers", 
               "israelis", 
               "family", 
               "soldiers", 
               "journalists", 
               "staff"),
  Count = c(43000, 
            41431, 
            39000,  # Example estimate for 90% civilians
            13000, 
            224, 
            1706, 
            825, 
            395, 
            116, 
            224) # Including humanitarian aid workers such as UNRWA staff
)
# Calculate the percentage for each category
summary_data <- summary_data %>%
  mutate(Percentage = (Count / sum(Count)) * 100)
```


| **Category**             | **Count**                                      |
|--------------------------|------------------------------------------------|
| People                   | 43,000                                         |
| Palestinians             | 41,431                                         |
| Civilians                | Estimated 90% (various reports), e.g., 815 civilians killed in October 7 attacks in Israel |
| Children                 | 13,000 (Gaza), 7,797 (UN confirmed identities) |
| Workers                  | 224 humanitarian aid workers, including 179 UNRWA employees |
| Israelis                 | 1,706 overall; 1,139 killed in October 7 attacks |
| Family                   | Over 60% of Gazans lost family members; 825 families killed entirely |
| Soldiers                 | 395 IDF soldiers killed                        |
| Journalist               | 116 (Committee to Protect Journalists), 134 (International Federation of Journalists) |
| Staff                    | 224 humanitarian aid workers, including 179 UNRWA employees|



```{r}
# Assuming you have both data frames `top10_filtered_long` and `summary_data` already prepared
# Adjust 'String' column to match the 'Category' for comparison purposes
# Ensure that 'String' and 'Category' are factors ordered by the Percentage in descending order
top10_filtered_long <- top10_filtered_long %>%
  mutate(String = factor(String, levels = unique(String[order(-Percentage)])))

summary_data <- summary_data %>%
  mutate(String = factor(String, levels = unique(String[order(-Percentage)])))
```


```{r}
# Add a DataType column to distinguish between the two datasets

summary_data <- summary_data %>%
  mutate(media = "Wikipedia")
```

```{r}
temp <- top10_filtered_long %>% select(String, Count, Percentage, media) %>% relocate(media, .after = Percentage)
top10_summary_combined <- rbind(temp
                                ,summary_data)
```


```{r}
plot <- ggplot() +
  geom_col(data = temp, aes( x = Percentage, y = String, fill = media, shape = media, group = media), alpha = 1,position="dodge") +
  geom_col(data = summary_data, aes(x = Percentage, y = String,color=media), alpha = 0.5)+
  #scale_color_manual(values = source_colors2) +
  scale_color_manual(values="darkgrey",
                     labels = paste("Wikipedia"," (people=",summary_data$Count[summary_data$String=="people"],")",sep = ""))+
  scale_fill_manual(values = source_colors2,
                    labels = c(paste("AJ"," (n=",length(en_AJ_killed_subjects_counts_df$String),")",sep = ""),
                              paste("BBC"," (n=",length(en_BBCNews_killed_subjects_counts_df$String),")",sep = ""),
                              paste("CNN"," (n=",length(en_CNN_killed_subjects_counts_df$String),")",sep = ""),
                              paste("DW"," (n=",length(en_DW_killed_subjects_counts_df$String),")",sep = ""))) +
  scale_shape_manual(values = source_shapes2) +
  labs(x = "Percentage", y = "Subjects", title = expression(paste("Most frequent Subjects of passive ", italic("killed")))) +
  scale_y_discrete(limits = rev(levels(top10_summary_combined$String)))+  # Reverse the y-axis to have the highest percentage at the top
  theme_minimal() +
#  theme(
#    panel.grid.major.x = element_blank(),  # Remove major vertical grid lines
#    panel.grid.minor.x = element_blank()   # Remove minor vertical grid lines
#  )# Add a legend
  theme(panel.grid = element_blank())  
plot <- plot+ guides(color = guide_legend(title = "relative reported casualties"))


plot

# Convert the ggplot to an interactive plotly plot
#ggplotly(plot)
```


```{r}
plot <- ggplot() +
    geom_col(data = summary_data, aes(x = Percentage, y = String,color=media), alpha = 0.7)+
  #scale_color_manual(values = source_colors2) +
  scale_color_manual(values="darkgrey",
                     labels = "source:")+
  geom_col(data = temp, aes( x = Percentage, y = String, fill = media, shape = media, group = media), alpha = 1,position="dodge") +
  geom_text(data = summary_data, aes(x = Percentage, y = String, label = Count), hjust=0,vjust = -1, size = 2.5)+
  scale_fill_manual(values = source_colors2,
                    labels = c(paste("AJ"," (n=",length(en_AJ_killed_subjects_counts_df$String),")",sep = ""),
                              paste("BBC"," (n=",length(en_BBCNews_killed_subjects_counts_df$String),")",sep = ""),
                              paste("CNN"," (n=",length(en_CNN_killed_subjects_counts_df$String),")",sep = ""),
                              paste("DW"," (n=",length(en_DW_killed_subjects_counts_df$String),")",sep = ""))) +
  scale_shape_manual(values = source_shapes2) +
  labs(x = "Percentage", y = "Subjects", title = expression(paste("Most frequent Subjects of passive ", italic("killed")))) +
  scale_y_discrete(limits = rev(levels(top10_summary_combined$String)))+  # Reverse the y-axis to have the highest percentage at the top
  theme_minimal() +
  coord_cartesian(xlim = c(min(summary_data$Percentage), max(summary_data$Percentage) + 2))+
#  theme(
#    panel.grid.major.x = element_blank(),  # Remove major vertical grid lines
#    panel.grid.minor.x = element_blank()   # Remove minor vertical grid lines
#  )# Add a legend
  theme(panel.grid = element_blank())  
plot <- plot+ guides(color = guide_legend(title = "relative reported casualties"))




# Read the QR code image
#qr_img <- jpeg::readJPEG("casualties_qr.jpg")
#qr_grob <- rasterGrob(qr_img, interpolate = TRUE)

# Add the QR code to the ggplot
#plot <- plot + annotation_custom(grob = qr_grob)

plot
#ggsave("Passive_killed_subjects.pdf", scale = 0.5, plot,  width = 42,
# height = 29.7, units="cm")
# Convert the ggplot to an interactive plotly plot
#ggplotly(plot)
```
