---
title: "Analysis in R"
author: "Lorenz Geiger"
date: "2024-09-07"
output: html_document
---

```{r clean_start}
rm(list = ls())

## Load required libraries 
require(tidyverse)

```
Results have been saved to data/en_DW/keyword_frequencies.csv
Total Frequencies Across All Files:
  israel Total Count: 19697
  israel Relative Frequency: 12587.33 instances per million
  gaza Total Count: 10317
  gaza Relative Frequency: 6593.06 instances per million
  hamas Total Count: 7001
  hamas Relative Frequency: 4473.98 instances per million
  people Total Count: 5951
  people Relative Frequency: 3802.98 instances per million
  israeli Total Count: 6385
  israeli Relative Frequency: 4080.32 instances per million
  know Total Count: 5901
  know Relative Frequency: 3771.02 instances per million
  war Total Count: 6228
  war Relative Frequency: 3979.99 instances per million
  think Total Count: 3803
  think Relative Frequency: 2430.30 instances per million
  hostages Total Count: 2494
  hostages Relative Frequency: 1593.79 instances per million
  iran Total Count: 3207
  iran Relative Frequency: 2049.43 instances per million
  Total Word Count Across All Files: 1564827


```{r}
en_AJ <- read.csv("frequency_data/en_AJ_frequency.csv")
en_BBCNews <- read.csv("frequency_data/en_BBCNews_frequency.csv")
en_CNN <- read.csv("frequency_data/en_CNN_frequency.csv")
en_DW <- read.csv("frequency_data/en_DW_frequency.csv")

```


```{r}
ggplot(en_DW, aes=())
```



